---
title: "vbaR"
author: "Chi Zhang"
date: "05/07/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Package(s) & Function(s)
```{r}
source("vbaFunc.R")
```

# Read in CSV file for generating input data
```{r pressure, echo=FALSE}
age_cohorts <- read.csv("./Input_CSV/age_cohorts.csv")
labels_other_key <- read.csv("./Input_CSV/labels_other_key.csv")
labels <- read.csv("./Input_CSV/labels.csv")
AgeSexERPs <- read.csv("./Input_CSV/AgeSexERPs.csv")
SmallAreaTotals <- read.csv("./Input_CSV/SmallAreaTotals.csv")
LifeExpectancy <- read.csv("./Input_CSV/LifeExpectancy.csv")
Mortality <- read.csv("./Input_CSV/Mortality.csv")
ASFR_Prelim <- read.csv("./Input_CSV/ASFR_Prelim.csv")
otherFertility <- read.csv("./Input_CSV/otherFertility.csv")
migRate <- read.csv("./Input_CSV/migRate.csv")
migTurnover <- read.csv("./Input_CSV/migTurnover.csv")
TotPopulation <- read.csv("./Input_CSV/TotPopulation.csv")
totBirth <- read.csv("./Input_CSV/totBirth.csv")
totDeath <- read.csv("./Input_CSV/totDeath.csv")
totNetMig <- read.csv("./Input_CSV/totNetMig.csv")
```

# Define Variables
```{r}
numareas = labels_other_key[1, 7]       # Number of small areas
numages = age_cohorts[18, 1]            # Number of age groups in ERPs
lastage = age_cohorts[18, 3]            # Number of period cohorts
final = labels_other_key[1, 6]          # Final projection year number
SRB = otherFertility[1, 3]              # Sex Ratio at Birth (Male : Female)
modelTFR  = otherFertility[1, 2]        # Model TFR Parameter
nLxMS = length(Mortality) - 2           # nLx mortality surface groups
age_ASFR = length(otherFertility[, 1])  # Age groups amount in ASFRs
smallnumber = 0.0001                    # Smoothed Number
maxqiter = labels_other_key[1, 4]       # Max number of population-at-risk loop iterations
maxziter = labels_other_key[1, 5]       # Max number of migration adjustment iterations
```

# xTRF
```{r}
# Read in jumpoffERP Data
jumpoffERP = jumpoffERP_Func(AgeSexERPs, numages, numareas, 6, 8)

# Generate xTFR vector for storing
result_xTFR = xTFR(jumpoffERP, numareas)
```

# PrepareData
## Start Generating Input Data
### Read in Data for Generating Input Data
```{r}
# Labels
Areacode = labels[, 2]
Areaname = labels[, 3]
agelabel = age_cohorts[, 2]
pclabel = age_cohorts[, 4]
sexlabel = totBirth[, 1]
yearlabel = labels_other_key[1:(final + 2), 1]
intervallabel = labels_other_key[1:(final + 1), 1]

# Estimated & Projected Small Area Total Population (Aggregated)
TotPop = t(SmallAreaTotals[, 4:5])

# ERP (Estimated Resident Population) by age & sex (before and at jumpoff year)
ERP = readERP(2, numareas, numages, AgeSexERPs, FALSE)

# Area-specific TFRs
TFR = data.frame(result_xTFR, result_xTFR, result_xTFR, result_xTFR)
colnames(TFR) = labels_other_key[1:(1+final), 2]
TFR = t(TFR)

# Read in data for ASFRs and Preliminary ASFRs (Area specific fertility Rate)
modelASFR = otherFertility[, 1]
prelimASFR = ASFR_Prelim

# Read in data for Life Expectancy and Mortality Surface
EM_Result = readLEMS(final, numareas, numages, nLxMS, LifeExpectancy, Mortality)
eO = EM_Result$eO
MS_nLx = EM_Result$MS_nLx
MS_TO = data.frame(cbind(t(Mortality[1+numages, 3:(3+nLxMS-1)]), t(Mortality[(1+numages)*2, 3:(3+nLxMS-1)])))

# Read in data of migration data and for ASMRs (Area specific Mortality Rate)
totmig = migTurnover[, 4]
modelASMR = t(migRate[, 2:3])
```

### Some Checks (Need further confirmation)
```{r}
# TFRs > 0
for (i in 1:(final + 1)){
  for (a in 1:numareas){
      if (TFR[i, a] < 0.1){
          print("Error: Year = ", yearlabel[i], " & Area = ", Areaname[a])
          break}}}

# eOs > 0
for (i in 1:(final + 1)){
  for (a in 1:numareas){
    for (q in 1:2){
        if (eO[i, a, q] < 0.1){
          print("Error: Year = ", yearlabel[i], " & Area = ", Areaname[a], " & Sex = ", sexlabel[q])
          break}}}}

# Check Migration Turnover > 0
for (i in 1:numareas){
  if (totmig[i] < 0.1){
    print("Error: Area =", Areaname[i])
    break}}
    
# Check Small Area Population Total > 0
for (i in 1:2){
  for (a in 1:numareas){
    if (TotPop[i, a] < 0.1){
      print("Error Year =", yearlabel[i], " & Area = ", Areaname[a])
      break}}}
```

### Calculate Input Data
```{r}
# Create input data for ASFR (Area specific Fertility Rate)
ASFR = inputASFR(final, numareas, age_ASFR, prelimASFR, modelASFR, TFR, modelTFR)

# Estimate base period birth by sex for the population 'Accounts'
tempbirth = inputbirth(numareas, age_ASFR, ASFR, ERP, SRB)
tempbirthssex = tempbirth$tempsex
temptotbirths = tempbirth$temp

# Calculate base period projected age-specific death rate (used in estimating death account)
ASDR = inputASDR(final, numareas, lastage, nLxMS, eO, MS_TO, MS_nLx)

# Calculate estimated death for age-sex cohorts and total population accounts
tempdeath = inputdeath(numareas, lastage, ASDR, ERP)
tempdeaths = tempdeath$deaths
temptotdeaths = tempdeath$totdeaths

# Calculate migration input data
migData = inputMigration(final, numareas, lastage, modelASMR, ERP, totmig, TotPop, temptotdeaths, temptotbirths,
                         tempdeaths, tempbirthssex, ASDR, Areaname, sexlabel, pclabel, intervallabel)
ASOMR = migData$ASOMR
inward = migData$inward
outward = migData$outward
prelimmig = migData$prelimmig
scaledmig = migData$scaledmig
prelimbaseinward = migData$prelimbaseinward
prelimbaseoutward = migData$prelimbaseoutward
cohortnetmig = migData$cohortnetmig
adjnetmig = migData$adjnetmig
scalingfactor2a = migData$scalingfactor2a
scalingfactor2b = migData$scalingfactor2b
```

### Write Input Data to Worksheet (Accounts)
```{r}
# Write to Accounts.csv
Accounts_area = rep(0, numareas * numages * 2)
Accounts_sex = rep(0, numareas * numages * 2)
Accounts_period_cohort = rep(0, numareas * numages * 2)
Accounts_ERP_tb = rep(0, numareas * numages * 2)
Accounts_Deaths = rep(0, numareas * numages * 2)
Accounts_Netmig = rep(0, numareas * numages * 2)
Accounts_ERP_tn = rep(0, numareas * numages * 2)
Accounts_prelimmig = rep(0, numareas * numages * 2)
Accounts_scaledmig = rep(0, numareas * numages * 2)
Accounts_prelimin = rep(0, numareas * numages * 2)
Accounts_prelimout = rep(0, numareas * numages * 2)
Accounts_scalingraw = rep(0, numareas * numages * 2)
Accounts_scalingsmooth = rep(0, numareas * numages * 2)
Accounts_inmig = rep(0, numareas * numages * 2)
Accounts_outmig = rep(0, numareas * numages * 2)
Accounts_adjmig = rep(0, numareas * numages * 2)

index = 0
for (i in 1:numareas){
  for (s in 1:2){
    for (a in 1:numages){
      index = index + 1
      
      if (s == 1){
        if (a == 1){
          Accounts_ERP_tb[index] = tempbirthssex[i, s]}
        else if (a == numages){
          Accounts_ERP_tb[index] = ERP[1, i, s, lastage] + ERP[1, i, s, lastage + 1]}
        else{
          Accounts_ERP_tb[index] = ERP[1, i, s, a - 1]}
        
        Accounts_area[index] = Areaname[i]
        Accounts_sex[index] = sexlabel[s]
        Accounts_period_cohort[index] = pclabel[a]
        Accounts_ERP_tn[index] = ERP[2, i, s, a]
        Accounts_Deaths[index] = tempdeaths[i, s, a]
        Accounts_Netmig[index] = cohortnetmig[i, s, a]
        Accounts_prelimmig[index] = prelimmig[i, s, a]
        Accounts_scaledmig[index] = scaledmig[i, s, a]
        Accounts_prelimin[index] = prelimbaseinward[i, s, a]
        Accounts_prelimout[index] = prelimbaseoutward[i, s, a]
        Accounts_scalingraw[index] = scalingfactor2a[i, s, a]
        Accounts_scalingsmooth[index] = scalingfactor2b[i, s, a]
        Accounts_inmig[index] = inward[1, i, s, a]
        Accounts_outmig[index] = outward[i, s, a]
        Accounts_adjmig[index] = adjnetmig[i, s, a]}
      
      else{
        if (a == 1){
          Accounts_ERP_tb[index] = tempbirthssex[i, s]}
        else if (a == numages){
          Accounts_ERP_tb[index] = ERP[1, i, s, lastage] + ERP[1, i, s, lastage + 1]}
        else{
          Accounts_ERP_tb[index] = ERP[1, i, s, a - 1]}
        
        Accounts_area[index] = Areaname[i]
        Accounts_sex[index] = sexlabel[s]
        Accounts_period_cohort[index] = pclabel[a]
        Accounts_ERP_tn[index] = ERP[2, i, s, a]
        Accounts_Deaths[index] = tempdeaths[i, s, a]
        Accounts_Netmig[index] = cohortnetmig[i, s, a]
        Accounts_prelimmig[index] = prelimmig[i, s, a]
        Accounts_scaledmig[index] = scaledmig[i, s, a]
        Accounts_prelimin[index] = prelimbaseinward[i, s, a]
        Accounts_prelimout[index] = prelimbaseoutward[i, s, a]
        Accounts_scalingraw[index] = scalingfactor2a[i, s, a]
        Accounts_scalingsmooth[index] = scalingfactor2b[i, s, a]
        Accounts_inmig[index] = inward[1, i, s, a]
        Accounts_outmig[index] = outward[i, s, a]
        Accounts_adjmig[index] = adjnetmig[i, s, a]}}}}

accounts_data = data.frame(Accounts_area, Accounts_sex, Accounts_period_cohort, Accounts_ERP_tb,
                           Accounts_Deaths, Accounts_Netmig, Accounts_ERP_tn, Accounts_prelimmig,
                           Accounts_scaledmig, Accounts_prelimin, Accounts_prelimout, Accounts_scalingraw,
                           Accounts_scalingsmooth, Accounts_inmig, Accounts_outmig, Accounts_adjmig)
colnames(accounts_data) <- c("Area", "Sex", "Period-Cohort", "ERP(t-5)", "Deaths", "Net mig", "ERP(t)", 
                             "Prelim mig (model rates x pop-at-risk)", "Scaled mig (adjusted for pop size)", 
                             "Prelim in (consistent with total net mig)", "Prelim out (consistent with total net mig)", 
                             "scaling factor a (unsmoothed)", "scaling factor b (smoothed)", 
                             "In-mig (consistent with cohort net mig)", "Out-mig (consistent with cohort net mig)", 
                             "Adjusted net mig")
write.csv(accounts_data, file = "./Output_CSV/Accounts.csv", row.names = FALSE)
```

### Write Input Data to Worksheet (SmallAreaInputs)
```{r}
# Write to SmallAreaInputs.csv
SmallAreaInputs_index = rep(0, numareas * numages)
SmallAreaInputs_code = rep(0, numareas * numages)
SmallAreaInputs_name = rep(0, numareas * numages)
SmallAreaInputs_pc = rep(0, numareas * numages)
SmallAreaInputs = cbind(SmallAreaInputs_index, SmallAreaInputs_code,
                        SmallAreaInputs_name, SmallAreaInputs_pc)

# Create Dataframe
for (info in 1:3){
  for (i in 1:final){
    for (s in 1:2){
      SmallAreaInputs = cbind(SmallAreaInputs, rep(0, numareas * numages))}}}
for (ASFR_col in 1:(final+1)){
  SmallAreaInputs = cbind(rep(NaN, numareas * numages))}
wb_wt_SmallAreaInputs = data.frame(SmallAreaInputs)

index = 0
for (i in 1:numareas){
  for (pc in 1:(lastage + 1)){
    index = index + 1
    
    wb_wt_SmallAreaInputs[index, 1] = i
    wb_wt_SmallAreaInputs[index, 2] = Areacode[i]
    wb_wt_SmallAreaInputs[index, 3] = Areaname[i]
    wb_wt_SmallAreaInputs[index, 4] = pclabel[pc]
    
    for (s in 1:2){
      for (year in 1:final){
        if (s == 1){
          wb_wt_SmallAreaInputs[index, 4 + year] = ASDR[year + 1, i, 1, pc]}
        else {
          wb_wt_SmallAreaInputs[index, 4 + final + year] = ASDR[year + 1, i, 2, pc]}}}
    
    for (s in 1:2){
      for (year in 1:final){
        if (s == 1){
          wb_wt_SmallAreaInputs[index, 4 + 2 * final + year] = ASOMR[year + 1, i, 1, pc]}
        else {
          wb_wt_SmallAreaInputs[index, 4 + 3 * final + year] = ASOMR[year + 1, i, 2, pc]}}}
    
    for (s in 1:2){
      for (year in 1:final){
        if (s == 1){
          wb_wt_SmallAreaInputs[index, 4 + 4 * final + year] = inward[year + 1, i, 1, pc]}
        else {
          wb_wt_SmallAreaInputs[index, 4 + 5 * final + year] = inward[year + 1, i, 2, pc]}}}
    
    if (pc > 4 & pc < 12){
      wb_wt_SmallAreaInputs[index, 4 + 6 * final + 1] = agelabel[pc - 1]
      for (year in 1:final){
        wb_wt_SmallAreaInputs[index, 4 + 6 * final + 1 + year] = ASFR[year + 1, i, pc - 4]}}}}

# Set column names
SAI_names = c()
for (s in 1:2){
  for (i in 1:final){
    if (s == 1){
      SAI_names = c(SAI_names, paste("F_ASDRs", labels_other_key[i+1, 2]))}
    else{
      SAI_names = c(SAI_names, paste("M_ASDRs", labels_other_key[i+1, 2]))}}}
for (s in 1:2){
  for (i in 1:final){
    if (s == 1){
      SAI_names = c(SAI_names, paste("F_ASOMRs", labels_other_key[i+1, 2]))}
    else{
      SAI_names = c(SAI_names, paste("M_ASOMRs", labels_other_key[i+1, 2]))}}}
for (s in 1:2){
  for (i in 1:final){
    if (s == 1){
      SAI_names = c(SAI_names, paste("F_inward", labels_other_key[i+1, 2]))}
    else{
      SAI_names = c(SAI_names, paste("M_inward", labels_other_key[i+1, 2]))}}}
SAI_names = c(SAI_names, "Age-Cohort")
for (i in 1:final){
  SAI_names = c(SAI_names, paste("ASFRs", labels_other_key[i+1, 2]))}

# Save SmallAreaInputs as CSV
colnames(wb_wt_SmallAreaInputs) <- c("Index", "Code", "Area", "Period-Cohort", SAI_names)
write.csv(wb_wt_SmallAreaInputs, file = "./Output_CSV/SmallAreaInputs.csv", row.names = FALSE)
```

# SyntheticProjectionModel
## Start Generating Projection Data
### Load in Required Input Data for Generating Projection Output
```{r}
# Read in Estimated & Projected Small Area Total Population (Aggregated)
TotPop = t(SmallAreaTotals[, 5:(5+final)])

# Read in small area ERP (Estimated Resident Population) by age & sex (at jumpoff year)
ERP = readERP(1, numareas, numages, AgeSexERPs, TRUE)

# Read in National population estimate & projections by age & sex
NatP = readNatP(final, numages, TotPopulation)

# Read in ASDR, ASOMR, Inward Migration, ASFR data for projection
ASDR = ASDR[2:(1+final), 1:numareas, 1:2, 1:numages]
ASOMR = ASOMR[2:(1+final), 1:numareas, 1:2, 1:numages]
inward = inward[2:(1+final), 1:numareas, 1:2, 1:numages]
ASFR = ASFR[2:(1+final), 1:numareas, 1:age_ASFR]

# Read in National projected births, deaths, net migration data
NatB = t(totBirth[1:2, 2:4])
NatDpc = readDN(final, lastage, numages, totDeath)
NatNpc = readDN(final, lastage, numages, totNetMig)
```

### Some Checks & Headings Writing
```{r}
# pop total > 0
for (y in 1:final){
  for (i in 1:numareas){
    if (TotPop[y, i] < 0.1){
      print("Error: Year = ", yearlabel[y + 2], " & Area = ", Areaname[i])
      break}}}

# Check small area population totals match national population total
for (y in 1:(final + 1)){
  checktot1 = 0
  for (i in 1:numareas){
    checktot1 = checktot1 + TotPop[y, i]}
  checktot2 = 0
  for (s in 1:2){
    for (a in 1:(lastage + 1)){
      checktot2 = checktot2 + NatP[y, s, a]}}
    
  if (abs(checktot1 - checktot2) > smallnumber){
    print("Error: Year = ", yearlabel[y + 1], "Sum of pop total = ", checktot1, ", Sum of national projections = ", checktot2)
    break}}

# Create Dataframe for CheckMig, CheckDeaths, Log
check_Sheet = writeNoteCL(lastage, pclabel, labels_other_key, final, Areaname, sexlabel)
wb_wt_Log = check_Sheet$Log
wb_wt_CheckMig = check_Sheet$Mig
wb_wt_CheckDeaths = check_Sheet$Deaths
```

### Projection
```{r}
# Set initial value of jump-off year population in age-sex cohort
Population = readIniPop(final, numareas, numages, ERP)

# Record total jump-off population into dataset for further projection usage
totPopulation = readIniTPop(final, numareas, numages, Population)

# Main Projection Section Starts
# Start the Projection Interval Loop (record final = 3 projection years)
Pop0 = array(rep(0, final * numareas * 2 * (lastage + 1)), dim = c(final, numareas, 2, (lastage + 1)))
Pop1 = array(rep(0, final * numareas * 2 * (lastage + 1)), dim = c(final, numareas, 2, (lastage + 1)))
Btot = array(rep(0, final * numareas), dim = c(final, numareas))                                       # Total Birth in sex cohort
Dpc = array(rep(0, final * numareas * 2 * (lastage + 1)), dim = c(final, numareas, 2, (lastage + 1)))  # Death in age-sex cohort
Dtot = array(rep(0, final * numareas), dim = c(final, numareas))                                       # Total Death in sex cohort
IMpc = array(rep(0, final * numareas * 2 * (lastage + 1)), dim = c(final, numareas, 2, (lastage + 1))) # Total Inward Migration in sex cohort
OMpc = array(rep(0, final * numareas * 2 * (lastage + 1)), dim = c(final, numareas, 2, (lastage + 1))) # Total Outward Migration in sex cohort
totN = array(rep(0, final * numareas), dim = c(final, numareas))
previousPop1 = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
totINMIG = array(rep(0, final * numareas), dim = c(final, numareas))
totOUTMIG = array(rep(0, final * numareas), dim = c(final, numareas))
```

### Projection Iteration
```{r}
for (y in 2:(final + 1)){
  # Record for each year of projection, the initial population is the previous year's projected population
  # This function does not record the projected pop of 0-4 group
  for (i in 1:numareas){
    for (s in 1:2){
      for (pc in 2:lastage){
        Pop0[y - 1, i, s, pc] = Population[y - 1, i, s, pc - 1]}
       
      # Record 85+ group population
      Pop0[y - 1, i, s, lastage + 1] = Population[y - 1, i, s, lastage] + Population[y - 1, i, s, lastage + 1]}}
 
  # Start large iteration
  for (q in 1:maxqiter){
     
    # Record the number of iteration required
    wb_wt_Log[y - 1, 2] = q
     
    # For the first iteration, the end-of-interval population is set (avoid a negative projected population)
    if (q == 1){
      for (i in 1:numareas){
        for (s in 1:2){
          for (pc in 1:lastage){
            Pop1[y - 1, i, s, pc + 1] = 0}}}} # (+++ Projection Data Pop1 is written +++)
     
    #--------------------------------------------------------------------------
    # Birth Projection
    # Preliminary birth by age of mother
    Bage = array(rep(0, numareas * age_ASFR), dim = c(numareas, age_ASFR))
    Btottmp = rep(0, numareas)
    for (i in 1:numareas){
      Btottmp[i] = 0
      for (pc in 1:7){
        Bage[i, pc] = ASFR[y - 1, i, pc] * 2.5 * (Pop0[y - 1, i, 1, pc + 4] + Pop1[y - 1, i, 1, pc + 3])
        Btottmp[i] = Btottmp[i] + Bage[i, pc]}}
     
    # Preliminary birth by sex
    Bsextmp = array(rep(0, numareas * 2), dim = c(numareas, 2))
    Bsextmptot =  rep(0, 2)
    for (i in 1:numareas){
      # Female
      Bsextmp[i, 1] = Btottmp[i] * (100 / (100 + SRB))
      Bsextmptot[1] = Bsextmptot[1] + Bsextmp[i, 1]
      # Males
      Bsextmp[i, 2] = Btottmp[i] * (SRB / (100 + SRB))
      Bsextmptot[2] = Bsextmptot[2] + Bsextmp[i, 2]}
    
    # Constrain to national births by sex (+++ Projection total birth -- Btot is Written +++)
    Bsex = array(rep(0, numareas * 2), dim = c(numareas, 2))
    for (i in 1:numareas){
      Btot[y - 1, i] = 0
      for (s in 1:2){
        Bsex[i, s] = Bsextmp[i, s] * NatB[y - 1, s] / Bsextmptot[s]
        Btot[y - 1, i] = Btot[y - 1, i] + Bsex[i, s]}}
    
    # Allocate births to the initial infant population (+++ Projection Pop0 is written for filling age-group 0-4 +++)
    for (i in 1:numareas){
      for (s in 1:2){
        Pop0[y - 1, i, s, 1] = Bsex[i, s]}}
    
    # For the first iteration, the end-of-interval group 0-4 population is set (+++ Pop1 is written fo filling group 0-4 +++)
    if (q == 1){
      for (i in 1:numareas){
        for (s in 1:2){
          Pop1[y - 1, i, s, 1] = Bsex[i, s]}}}
    
    #---------------------------------------------------------------------------
    # Death Projection
    # Preliminary deaths in age-sex groups
    Dtmp = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    for (i in 1:numareas){
      for (s in 1:2){
        # Record age group without 0-4
        for (pc in 2:(lastage + 1)){
          Dtmp[i, s, pc] = ASDR[y - 1, i, s, pc] * 2.5 * (Pop0[y - 1, i, s, pc] + Pop1[y - 1, i, s, pc])}
          # Record age group 0-4    
        Dtmp[i, s, 1] = ASDR[y - 1, i, s, 1] * 2.5 * Pop1[y - 1, i, s, 1]}}
    
    # Preliminary total deaths (sum age)
    Dtmptot = array(rep(0, 2 * (lastage + 1)), dim = c(2, (lastage + 1)))
    for (i in 1:numareas){
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          Dtmptot[s, pc] = Dtmptot[s, pc] + Dtmp[i, s, pc]}}}
    
    # Constrain to national deaths (+++ Dpc, Dtot are written as death projection data +++)
    for (i in 1:numareas){
      Dtot[y - 1 , i] = 0
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          Dpc[y - 1, i, s, pc] = Dtmp[i, s, pc] * NatDpc[y - 1, s, pc] / Dtmptot[s, pc]
          Dtot[y - 1, i] = Dtot[y - 1, i] + Dpc[y - 1, i, s, pc]}}}
    
    #---------------------------------------------------------------------------
    # Migration Projection
    # Preliminary Migration (in & out)
    prelimIMpc = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    prelimOMpc = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    for (i in 1:numareas){
      for (s in 1:2){
        # Record age group without 0-4
        for (pc in 2:(lastage + 1)){
          prelimIMpc[i, s, pc] = inward[y - 1, i, s, pc]
          prelimOMpc[i, s, pc] = ASOMR[y - 1, i, s, pc] * 2.5 * (Pop0[y - 1, i, s, pc] + Pop1[y - 1, i, s, pc])}
        # Record age group 0-4
        prelimIMpc[i, s, 1] = inward[y - 1, i, s, 1]
        prelimOMpc[i, s, 1] = ASOMR[y - 1, i, s, 1] * 2.5 * Pop1[y - 1, i, s, 1]}}
    
    # Calculate residual net migration required to produce total projected populations
    requiredN = rep(0, numareas)
    for (i in 1:numareas){
      requiredN[i] = TotPop[y, i] - TotPop[y - 1, i] - Btot[y - 1, i] + Dtot[y - 1, i]}
    
    # Preparing arrays for IPF
    NatN = array(rep(0, 2 * (lastage + 1)), dim = c(2, (lastage + 1)))
    for (s in 1:2){
      for (pc in 1:(lastage + 1)){
        NatN[s, pc] = NatNpc[y - 1, s, pc]}}
    
    LocalPop0 = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    LocalDpc = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    for (i in 1:numareas){
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          LocalPop0[i, s, pc] = Pop0[y - 1, i, s, pc]
          LocalDpc[i, s, pc] = Dpc[y - 1, i, s, pc]}}}
    
    labelint = intervallabel[y]
    labely = y
    labelq = q
    
    # Generate IPF
    scaledIM = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    scaledOM = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    
    # Call the NetMigAdjustment2 function to generate IPF data (scaled Inward & Outward Migration)
    scaledIO = NetMigAdjustment2(labely, prelimIMpc, prelimOMpc, NatN, requiredN, LocalPop0, LocalDpc, scaledIM,
                                 scaledOM, numareas, lastage, maxziter, smallnumber, wb_wt_Log)
    scaledIM = scaledIO$IM
    scaledOM = scaledIO$OM
    wb_wt_Log = scaledIO$Log
    
    # Allocate fitted migration to migration arrays (+++ IMpc, OMpc are written +++)
    for (i in 1:numareas){
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          IMpc[y - 1, i, s, pc] = scaledIM[i, s, pc]
          OMpc[y - 1, i, s, pc] = scaledOM[i, s, pc]}}}
    
    # END-OF-INTERVAL POPULATIONS
    for (i in 1:numareas){
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          Pop1[y - 1, i, s, pc] = Pop0[y - 1, i, s, pc] - Dpc[y - 1, i, s, pc] + IMpc[y - 1, i, s, pc] - OMpc[y - 1, i, s, pc]}}}
    
    # Difference between the end-of-interval population calculated above & Those of the previous iteration are compared
    totpop1_OK = 0
    pop1_OK = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    discrepancy = array(rep(0, numareas * 2 * (lastage + 1)), dim = c(numareas, 2, (lastage + 1)))
    if (q > 1){
      for (i in 1:numareas){
        for (s in 1:2){
          for (pc in 1:(lastage + 1)){
            discrepancy[i, s, pc] = abs(Pop1[y - 1, i, s, pc] - previousPop1[i, s, pc])
            if (discrepancy[i, s, pc] < smallnumber){
              pop1_OK[i, s, pc] = 0}
            else{
              pop1_OK[i, s, pc] = 1}
            totpop1_OK = totpop1_OK + pop1_OK[i, s, pc]}}}}
    
    # Previous iteration loop value of the final population are updated
    for (i in 1:numareas){
      for (s in 1:2){
        for (pc in 1:(lastage + 1)){
          previousPop1[i, s, pc] = Pop1[y - 1, i, s, pc]}}}
    
    # Convergence Check
    if (q > 1){
      if (totpop1_OK == 0){
        break}}}
    
  # Write out preliminary and scale net migration
  row = 0 + (y - 2) * (2 * (lastage + 1))
  for (s in 1:2){
    for (pc in 1:(lastage + 1)){
      row = row + 1
      col = 3
      for (i in 1:numareas){
        col = col + 1
        wb_wt_CheckMig[row, col] = prelimIMpc[i, s, pc] - prelimOMpc[i, s, pc]
        wb_wt_CheckMig[row, col + numareas] = IMpc[y - 1, i, s, pc] - OMpc[y - 1, i, s, pc]}
      col = col + 1
      wb_wt_CheckMig[row, col + numareas] = NatNpc[y - 1, s, pc]}}
  
  # Write out projected deaths
  row = 0 + (y - 2) * (2 * (lastage + 1))
  for (s in 1:2){
    for (pc in 1:(lastage + 1)){
      row = row + 1
      col = 3
      for (i in 1:numareas){
        col = col + 1
        wb_wt_CheckDeaths[row, col] = Dpc[y - 1, i, s, pc]}
      col = col + 1
      wb_wt_CheckDeaths[row, col] = NatDpc[y - 1, s, pc]}}
  
  # Calculate total migration for population accounts output
  for (i in 1:numareas){
    totN[y - 1, i] = 0
    totINMIG[y - 1, i] = 0
    totOUTMIG[y - 1, i] = 0
    for (s in 1:2){
      for (pc in 1:(lastage + 1)){
        totN[y - 1, i] = totN[y - 1, i] + (IMpc[y - 1, i, s, pc] - OMpc[y - 1, i, s, pc])
        totINMIG[y - 1, i] = totINMIG[y - 1, i] + IMpc[y - 1, i, s, pc]
        totOUTMIG[y - 1, i] = totOUTMIG[y - 1, i] + OMpc[y - 1, i, s, pc]}}}
  
  # Adjustment of age subscripts (+++ Population is written +++)
  for (i in 1:numareas){
    for (s in 1:2){
      for (pc in 1:(lastage + 1)){
        Population[y, i, s, pc] = Pop1[y - 1, i, s, pc]}}}
  
  # Total populations summed from age-sex populations (+++ totPopulation is written +++)
  for (i in 1:numareas){
    totPopulation[y, i] = 0
    for (s in 1:2){
      for (a in 1:numages){
        totPopulation[y, i] = totPopulation[y, i] + Population[y, i, s, a]}}}
  
  # Check for negative populations
  for (i in 1:numareas){
    for (s in 1:2){
      for (a in 1:numages){
        if (Population[y, i, s, a] < 0){
          print("Error: Negative population detected in one or more age groups")}}}}
}

# Write Check Data (Log, Mig, Deaths)
write.csv(wb_wt_Log, "./Output_CSV/Log.csv", row.names = FALSE)
write.csv(wb_wt_CheckDeaths, "./Output_CSV/CheckDeaths.csv", row.names = FALSE)
write.csv(wb_wt_CheckMig, "./Output_CSV/CheckMig.csv", row.names = FALSE)
```

### Write Projection Data (AgeSexForecases)
```{r}
AgeSexForecasts_index = rep(NaN, numareas * 2 * numages)
AgeSexForecasts_code = rep(NaN, numareas * 2 * numages)
AgeSexForecasts_name = rep(NaN, numareas * 2 * numages)
AgeSexForecasts_sex = rep(NaN, numareas * 2 * numages)
AgeSexForecasts_age = rep(NaN, numareas * 2 * numages)

AgeSexForecasts = cbind(AgeSexForecasts_index, AgeSexForecasts_code, AgeSexForecasts_name, AgeSexForecasts_sex, AgeSexForecasts_age)
for (i in 1:(1 + final)){
  AgeSexForecasts = cbind(AgeSexForecasts, rep(0, numareas * 2 * numages))}
wb_wt_AgeSexForecasts = data.frame(AgeSexForecasts)

row = 0
for (i in 1:numareas){
  for (s in 1:2){
    for (a in 1:numages){
      row = row + 1
      wb_wt_AgeSexForecasts[row, 1] = i
      wb_wt_AgeSexForecasts[row, 2] = Areacode[i]
      wb_wt_AgeSexForecasts[row, 3] = Areaname[i]
      wb_wt_AgeSexForecasts[row, 4] = sexlabel[s]
      wb_wt_AgeSexForecasts[row, 5] = agelabel[a]
      col = 5
      for (y in 1:(final + 1)){
        col = col + 1
        wb_wt_AgeSexForecasts[row, col] = Population[y, i, s, a]}}}}

colnames(wb_wt_AgeSexForecasts) <- c("No.", "Code", "Area name", "Sex", "Age group", yearlabel[2:(final+2)])
write.csv(wb_wt_AgeSexForecasts, "./Output_CSV/AgeSexForecasts.csv", row.names = FALSE)
```

### Write Projection Data (AgeSexForecases)
```{r}
components_info = rep(NaN, numareas * (1 + 5))
for (i in 1:final){
  components_info = cbind(components_info, rep(NaN, numareas * (1 + 5)))}
wb_wt_Components = data.frame(components_info)
colnames(wb_wt_Components) = c("Info", labels_other_key[(1+1):(1+final), 2])

row = 0
for (i in 1:numareas){
  row = row + 1
  wb_wt_Components[row, 1] = paste(as.character(i), Areaname[i])
  wb_wt_Components[row + 1, 1] = "Start-of-period population"
  wb_wt_Components[row + 2, 1] = "Births"
  wb_wt_Components[row + 3, 1] = "Deaths"
  wb_wt_Components[row + 4, 1] = "Net migration"
  wb_wt_Components[row + 5, 1] = "End-of-period population"
  
  col = 1
  for (y in 2:(final+1)){
    col = col + 1
    wb_wt_Components[row + 1, col] = totPopulation[y - 1, i]
    wb_wt_Components[row + 2, col] = Btot[y - 1, i]
    wb_wt_Components[row + 3, col] = Dtot[y - 1, i]
    wb_wt_Components[row + 4, col] = totN[y - 1, i]
    wb_wt_Components[row + 5, col] = totPopulation[y, i]}
  row = row + 5}

write.csv(wb_wt_Components, "./Output_CSV/Components.csv", row.names = FALSE)
```